\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-30 OaklandSubmission/ex.tex

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). E.g., in Figure~\ref{fig:ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the dot product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}).

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-componenets. For example,
the compiler realizes that the dot product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend})\footnote{In our usage of ABY, boolean is synonymous
  with Yao (Section~\ref{sec:impl}).}.

>>>>

The compiler splits the input
program into \emph{public} and \emph{secret} components. The public
components translate into regular C++ code, while the secret
components translate into API calls into our \mpc back-end
(ABY). E.g., in Figure~\ref{fig:ex-sml}, the \tool
compiler realizes that the array index \ls{i} in the inner product loop
is public, and hence the access locations need not be hidden.
Therefore, it compiles the \ls{for}~loop into a C++
\ls{for}~loop that will be executed in-clear
(line~\ref{line:dotproductloop}).

Within the secret components, the \tool compiler is ``cryptographic
cost-aware'', and appropriately picks either arithmetic or boolean
circuit representations for different sub-componenets. For example,
the compiler realizes that the inner product computation is more
efficient in the arithmetic representation, and therefore it builds
the corresponding circuit using the arithmetic circuit builder
\ls{acirc} (lines~\ref{line:dotmulgate} and~\ref{line:dotaddgate}). On
the other hand, since the comparison with \ls{b}, and the conditional
expression computation are more efficient in the boolean
representation, the \tool compiler uses the Yao circuit builder
\ls{ycirc} to build the corresponding circuits
(lines~\ref{line:condyaobegin} to~\ref{line:condyaoend})\footnote{In our usage of ABY, boolean is synonymous
  with Yao (Section~\ref{sec:impl}).}.

### 2017-10-30 OaklandSubmission/main.tex
small change
wip in S2
minor

\maketitle
% \begin{abstract}
% The abstract goes here.
% \end{abstract}
\IEEEpeerreviewmaketitle

@@

\input{intro}
%\input{fig-ex-sml}
\input{fig-ex-aby}

@@

\newpage
\bibliographystyle{abbrv}
\bibliography{bib}
\balance

>>>>

\maketitle
\begin{abstract}
Secure two-party computation (\mpc) allows two mutually distrusting parties to compute any function on their joint inputs, without revealing anything other than the output of the function to one another. %While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat.
% Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning classification tasks); or c) required cryptographers to design hand-crafted protocols for various applications.
 In this work, we present \tool: a 
%new ``cryptographic-cost aware'' 
\mpc framework that generates efficient and scalable \mpc protocols from high-level programs that 
%contain absolutely no cryptographic details. Programs in our language 
are easy-to-write and are statically verified. 
%Furthermore, 
The \mpc protocols generated by our framework match or outperform recent works that provide hand-crafted \mpc protocols for various functionalities such as classification and matrix factorization (up to a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle

@@

\input{intro}
%\input{fig-ex-sml}
%\input{fig-ex-aby}

@@

%\newpage
\bibliographystyle{abbrv}
\bibliography{bib}
%\balance
